Learning Actionable Analytics (with applications for reducing defects and reducing runtimes)

### 2015-05-07 related.tex
Updates from ShareLaTeX

The  difficulties associated with Hill's criteria lead Granger~\cite{granger80}
to propose another more practical criteria\footnote{Granger  himself comments that
his proposal was based on earlier work by Norbert Weiner~\cite{Seth2007}.}.
\mbox{G-causality} is based on building predictions based on {\em past} data,
then showing that this works for {\em future} data~\cite{granger80}. 
 In  \fig{work}, we demand that the {\em test}
data is not necessarily collected before the {\em train} data:
\bi
\item[\#1:] For data collected from software released in multiple versions, we should hence use  versions  $i,j$ to build models that are applied to version  $k$ where $i<j<k$.
\item[\#2:] For data collected from Monte Carlo simulations (where inputs are selected at random)
then as long as simulation $i$ is not used to adjust simulation $j> i$, then any item in that
data could be generated before any other. For this kind of data, we  can use the first $X\%$
of the simulation for training, and the remaining data for testing.
\ee
In the two case studies of this paper, the Jureczko object-oriented defect data comes from software
released in multiple versions while the Seigmund configuration data comes from Monte Carlo simulations.
Hence, we use procedure \#1 for the defect data and procedure \#2 for the configuration data.

>>>>

The  difficulties associated with Hill's criteria lead Granger~\cite{granger80}
to propose another more practical criteria\footnote{Granger  himself comments that
his proposal was based on earlier work by Norbert Weiner~\cite{Seth2007}.}.
\mbox{G-causality} is based on building predictions based on {\em past} data,
then showing that this works for {\em future} data~\cite{granger80}. 
 In  \fig{work}, we demand that the {\em test}
data is not necessarily collected before the {\em train} data:
\bi
\item[\#1:] For data collected from software released in multiple versions, we should hence use  versions  $i,j$ to build models that are applied to version  $k$ where $i<j<k$.
\item[\#2:] For data collected from Monte Carlo simulations (where inputs are selected at random)
then as long as simulation $i$ is not used to adjust simulation $j> i$, then any item in that
data could be generated before any other. For this kind of data, we  can use the first $X\%$
of the simulation for training, and the remaining data for testing.
\ei
In the two case studies of this paper, the Jureczko object-oriented defect data comes from software
released in multiple versions while the Seigmund configuration data comes from Monte Carlo simulations.
Hence, we use procedure \#1 for the defect data and procedure \#2 for the configuration data.
